[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

# Data {#sec-data}

## Data Description
The data sets for same and opposite-sex couples were derived from the *Office for National Statistics in the United Kingdom* with the 2020 edition of the “Marriages in England and Wales” workbook as raw data. This data is collected at the time a marriage is registered as part of civil registration which is a legal requirement in completing a legally recognized marriage in England and Wales. Annual marriage statistics are available to the public approximately two years after the end of the reference year [@statsguide]. Notably, same-sex couples that are currently in a civil partnership can have it converted to a marriage but these numbers are not counted towards the marriage statistics of same-sex couples in the workbook. The data collected and used in this paper is used to measure the number of couples that opt for civil or religious marriage ceremonies on a yearly basis [@statsguide].

@@

# Results {#sec-results}
Looking at the graphed data and summary statistics, there appears to be a clear decline in the number of opposite-sex couples opting for a religious ceremony across a fifty-year timeframe between 1970 and 2020. For same-sex couples, civil ceremonies have consistently and overwhelmingly been the most popular ceremony type since the legalization of same-sex marriage in 2014. The latter phenomenon is likely best explained by the relationship between religion and homophobia. Barbara Finlay and Carol S. Walter’s work in *Review of Religious Research* found that Protestants had the highest homophobia scores followed by Catholics, other Christian denominations, and other religions [@homophobiaresearch]. As same-sex religious ceremonies are conducted and approved by each religious authority [@statsguide], it could be possible that religious leaders do not approve of same-sex marriages. Another reason for the lack of same-sex religious ceremonies could also be non-heterosexual individuals moving away from religiosity due to conflicts between religious thought and their sexual identities.

## Opposite-Sex Religious Ceremony Type
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustype
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England (Red), Roman Catholic (Blue), Other Christian Denominations (Green), and Other Relgion Ceremonies (Purple) Conducted Between 1970 and 2020 in England and Wales for Opposite-Sex Couples

ggplot(opposite_sex, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color="steelblue")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1970, 2020, 5)) +
  scale_y_continuous(breaks = seq(0, 175000, 15000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

# Discussion {#sec-discussion}
## First discussion point {#sec-first-point}
## Second discussion point
## Third discussion point
## Weaknesses and Future Research {#sec-future}

>>>>

# Data {#sec-data}
## Data Description
The data sets for same and opposite-sex couples were derived from the *Office for National Statistics in the United Kingdom* with the 2020 edition of the “Marriages in England and Wales” workbook as raw data. This data is collected at the time a marriage is registered as part of civil registration which is a legal requirement in completing a legally recognized marriage in England and Wales. Annual marriage statistics are available to the public approximately two years after the end of the reference year [@statsguide]. Notably, same-sex couples that are currently in a civil partnership can have it converted to a marriage but these numbers are not counted towards the marriage statistics of same-sex couples in the workbook. The data collected and used in this paper is used to measure the number of couples that opt for civil or religious marriage ceremonies on a yearly basis [@statsguide].

@@

# Results {#sec-results}
Looking at the graphed data and summary statistics, there appears to be a clear decline in the number of opposite-sex couples opting for a religious ceremony across a fifty-year timeframe between 1970 and 2020. For same-sex couples, civil ceremonies have consistently and overwhelmingly been the most popular ceremony type since the legalization of same-sex marriage in 2014.

## Opposite-Sex Religious Ceremony Type
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustype
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England (Red), Roman Catholic (Yellow), Other Christian Denominations (Green), and Other Relgion Ceremonies (Purple) Conducted Between 1970 and 2020 in England and Wales for Opposite-Sex Couples

ggplot(opposite_sex, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color="yellow")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1970, 2020, 5)) +
  scale_y_continuous(breaks = seq(0, 175000, 15000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustypeten
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England (Red), Roman Catholic (Yellow), Other Christian Denominations (Green), and Other Relgion Ceremonies (Purple) Conducted Between 2010 and 2020 in England and Wales for Opposite-Sex Couples

ten_year <- subset(opposite_sex, year >= 2010 & year <= 2020)
ggplot(ten_year, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color="yellow")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2010, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 60000, 5000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

# Discussion {#sec-discussion}
## Implication: Religiosity has decreased in England and Wales
## Implication: Same-Sex Couples Overwhelmingly Prefer Civil Ceremonies
## Implication: 
## Limitations
## Future Research {#sec-future}
